Arc Blanc: a real time ocean simulation framework

### 2025-02-06 paper.tex
Fixed typos

Second, as \framework simulates a tile of water of size $N\times N$ using $c$ cascades, it stores the height, the displacement, and other relevant data in a 1D array of size $c$, where each entry contains a vector of 2D arrays of size $N\times N$. \Framework compute efficiently these values on the GPU, with dedicated kernel that are launched with a grid of threads structured as $N \times N \times c$. Specifically, $N \times N$ threads are assigned to the $x$ and $y$ dimensions to cover the spatial resolution of the water tile, while $c$ threads along the $z$ dimension correspond to the different cascades. This approach ensures that computations for all cascades are executed in parallel.

@@

\subsubsection{Drag Force}
\label{subsubsec:dragForce}
\Framework calculates drag forces based on the relative velocity between the fluid medium (water or air) and the submerged or exposed portion of the body. This approach is inspired by previous works \cite{yukselRealtimeWaterWaves2010,kellomakiRigidBodyInteraction2014,kernerWaterInteractionModel2016}.

>>>>

Second, as \framework simulates a tile of water of size $N\times N$ using $c$ cascades, it stores the height, the displacement, and other relevant data in a 1D array of size $c$, where each entry contains a 2D array of size $N\times N$. \Framework computes efficiently these values on the GPU, with dedicated kernel that are launched with a grid of threads structured as $N \times N \times c$. Specifically, $N \times N$ threads are assigned to the $x$ and $y$ dimensions to cover the spatial resolution of the water tile, while $c$ threads along the $z$ dimension correspond to the different cascades. This approach ensures that computations for all cascades are executed in parallel.

@@

\subsubsection{Drag Forces}
\label{subsubsec:dragForce}
\Framework calculates drag forces based on the relative velocity between the fluid medium (water or air) and the submerged or exposed portion of the body. This approach is inspired by previous works \cite{yukselRealtimeWaterWaves2010,kellomakiRigidBodyInteraction2014,kernerWaterInteractionModel2016}.
